\nazev{Penny Dreadful}[by={Skyclad},sr={1996 – Irrational Anthems}]

\capo{2}

\beginverse 
\nolyrics \[F Em D Am] \rep{4}
\endverse

\beginverse                      
\[Am]Forgive me if \[G]I'm out of \[Am]order                      
this new “music” \[G]has no \[Am]soul.                        
It may be good for \[G]making \[Am]money,                     
Sadly that is \[G]not my \[Am]goal.
\vspace{1em}                     
\[F]Integrity and \[Em]honesty are
\[D]words that you don't \[G]under\[Am]stand but
\[F]you're the best, it \[Em]says so in the
\[D]penny dreadful \[G]in your \[Am]hand.
\endverse

\beginchorus               
I saw you in the \[G]maga\[Am]zine,                        
they're calling you me\[G]ssi\[Am]ah.                       
they must be living \[G]in a \[Am]dream                    
they couldn't be \[G]more \[Am]wrong.
\endchorus

\beginverse 
\nolyrics \[F Em D Am] \rep{2}
\endverse

\beginverse
\[G]If we'd played this riff more punk,                                    
than may be we'd have had a million \[Am]seller.
\[G]But this piper's tune is not for sale,                                     
I'm glad to say I'm not that kind of \[Am]fella.
\[C]DJs, VJs, pimps and trollops,                                   
never mind music, this is bollocks.\[Am]
\endverse

\rechorus

\beginverse
\nolyrics {\[Am \hspace{2em} G Am] \rep{4}}
\vspace{1em}
\[F]turn on, \[Em]tune up, \[D]cash in, \[Am]sell out.                      
\[F]turn on, \[Em]tune up, \[D]cash in, \[Am]sell out.
\endverse


\beginverse
\chordsoff                         
\[Am]Stand your ground \[G]behind the \[Am]times                   
and refuse to \[G]follow \[Am]fashion.                    
Write your poe\[G]try with \[Am]anger,                      
and then sing it \[G]with a \[Am]passion.
\vspace{1em}                                  
\[F]Painted faces \[Em]in a circus,
\[D]images that \[G]spring to \[Am]mind,                          
\[F]when I read my \[Em]penny dreadful 
\[D]filled with pictures \[G]of your \[Am]kind.
\endverse

\rechorus

\beginverse 
\nolyrics \[F Em D Am] \rep{2}
\endverse

\beginverse
                    
Com\[G]mercial suicide's appealing after
ten years on this losing \[Am]streak
'Cause I'd \[G]rather be called sour and bitter
then be deemed the flavour of the \[Am]week.
\endverse

\rechorus

\beginverse \chordsoff
%\begin{center}
    \textit{Extra, extra, read all about it!}
%\end{center}
\endverse

\rechorus

\endsong