\nazev{Snuff}[by={Slipknot},sr={2008 – All Hope Is Gone}]

\capo{2}

\gtab{Hmi}{220XXX:000000}

\beginverse                        
\[Emi]Bury all your secrets \[Hmi]in my \[C]skin\[Hmi]                                         
\[Emi]Come away with innocence, \[Hmi]and l\[C]eave me with my sins\[Hmi]
\[Emi]The air around me still feels \[Hmi]like a \[C]cage\[Hmi]                                        
\[Emi]And love is just a camouflage \[Hmi]for \[C]what resembles rage \[Hmi Emi]again...
\endverse
  
\beginchorus

So if you love me, let me \[D]go.
And run away before I \[Emi]know.                                             
My heart is just too dark to \[D]care.
I can't destroy what isn't \[Emi]there.                                               
Deliver me into my \[D]Fate
If I'm alone I cannot \[Emi]hate                      
I don't deserve to have \[D]you...
My \[C]smile was taken long ago.
If I can change I hope I \[Hmi]never \[Emi]know
\endchorus

\chordsoff
\beginverse
I still press your letters to my lips
And cherish them in parts of me that savor every kiss
I couldn't face a life without your light
But all of that was ripped apart... when you refused to fight
\endverse

\beginchorus
So save your breath, I will not hear.
I think I made it very clear.
You couldn't hate enough to love.
Is that supposed to be enough?
I only wish you weren't my friend.
Then I could hurt you in the end.
I never claimed to be a Saint...
My own was banished long ago.
It took the Death of Hope to let you go
\endchorus

\beginchorus
So break yourself against my stones
And spit your pity in my soul
You never needed any help
You sold me out to save yourself
And I won't listen to your shame
You ran Away - you're all the same
Angels lie to keep control...
My love was punished long ago
If you still care, don't ever let me know
If you still care, don't ever let me know...
\endchorus

\endsong